\begin{thebibliography}{7}
 \addcontentsline{toc}{chapter}{Bibliografia}
\bibitem{bagus23}
	Bagus P., Howden D. [2009], 
	\emph{Qualitative Easing in support of a~tumbling financial system: a~look at the eurosystem's recent balance sheet policies}, Economic Affairs, Vol. 29, Issue 4, 60-65.	 
\bibitem{bernanke11}
	Bernanke B. S. [2010],
	\emph{The Economic Outlook and Monetary Policy}, \url{https://www.federalreserve.gov/newsevents/speech/bernanke20100827a.pdf},
	 System Rezerwy Federalnej, Jackson Hole, dostęp: styczeń 2017.
\bibitem{bernanke18}
	Bernanke B. S. [2013],
	\emph{Transcript of Chairman Bernanke’s Press Conference}, \url{http://www.federalreserve.gov/mediacenter/files/FOMCpresconf20130619.pdf},
	 System Rezerwy Federalnej, Waszyngton, dostęp: styczeń 2017.
\bibitem{bhattarai36}
	Bhattarai S., Chatterjee A. , Park W. Y. [2015], 
\emph{Effects of US Quantitative Easing on Emerging Market Economies},  \url{http://www.dallasfed.org/assets/documents/institute/wpapers/2015/0255.pdf}, Bank Rezerwy Federalnej w~Dallas, Dallas, dostęp: styczeń 2017.
\bibitem{chadha03} 
	Chadha J., Waters A. [2011],
	\emph{Quantitative Easing and Bond Yields: Results from a Macro-Finance Yield Curve}, \url{https://editorialexpress.com/cgi-bin/conference/download.cgi?db_name=CEF2011&paper_id=307}, Kent, dostęp: styczeń 2017.
\bibitem{chen36} 
Chen Q., Filardo A., He D., Zhu F. [2016],
\emph{Financial crisis, US unconventional monetary policy and international spillovers}, Journal of International Money and Finance, Vol.67, s.62-81.
\bibitem{christensen04}
	Christensen J., Rudebusch G. [2012],
	\emph{The Response of Interest Rates to U.S. and U.K. Quantitative Easing}, \url{http://www.frbsf.org/economic-research/files/wp12-06bk.pdf}, Bank Rezerwy Federalnej San Francisco, San Francisco, dostęp: styczeń 2017.	
\bibitem{christensen21}
Christensen J., Krogstrup S. [2016], 
\emph{Unconventional Monetary Policy: Lessons for the Transmission of Quantitative Easing}, \url{http://www.frbsf.org/economic-research/files/wp2014-18.pdf}, Bank Rezerwy Federalnej San Francisco, San Francisco, dostęp: styczeń 2017.
\bibitem{davtyan35}
Davtyan K. [2016], 
\emph{The Distributive Effects of Conventional and Unconventional Monetary Policies}, \url{http://www.ub.edu/irea/working_papers/2016/201606.pdf}, Instytut Badań nad Stosowaną Regionalną i~Publiczną Ekonomią, Barcelona, dostęp: styczeń 2017.	
\bibitem{ebc22}
Europejski Bank Centralny [2004], \textit{The Longer Term Refinancing Operations of the EBC}, \url{http://www.ecb.int/pub/pdf/scpwps/ecbwp359.pdf}, Frankfurt, dostęp: styczeń 2017.
\bibitem{gagnon34}
Gagnon J., Raskin M., Remache J., Sack B. [2011],
	\emph{The Financial Market Effects of the Federal Reserve's Large-Scale Asset Purchases}, International Journal of Central Banking, Vol. 7, 3-43. 
\bibitem{gambacorta35}
Gambacorta L., Hofmann B., Peersman G. [2014],
	\emph{The Effectiveness of Unconventional Monetary Policy at the Zero Lower Bound: A Cross-Country Analysis}, Journal of Money, Credit and Banking, Vol. 46, 615-642. 
\bibitem{kagraoki05}
Kagraoki Y., Moussa Z. [2010],
	\emph{Quantitative Easing, Credibility and the Time-Varying Dynamics of the Term Structure of Interest rate in Japan},
	Journal of International Financial Markets, Institutions and Money, Vol. 25, 181–201.
\bibitem{megg23}	
Meggyesi P. [2010],
 	\emph{Reflections on negative interest rates in
Switzerland}, \url{https://snbchf.com/wp-content/uploads/2012/10/JP-Morgan-on-Negative-Interests.pdf}, J.P. Morgan, Nowy York, dostęp: styczeń 2017.		
\bibitem{nelson01}
 	Nelson C. R., Siegel A.F. [1987], 
  	\emph{Parsimonious Modeling  of  Yield  Curves}, 
  	Journal  of Business, Volume 60, 473-489.
\bibitem{Fed09}
 	System Rezerwy Federalnej [2008],
 	\emph{Notatka prasowa z dnia 25. listopada 2008 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20081125b.htm}, Waszyngton, dostęp: styczeń 2017.	
\bibitem{Fed10}
 	System Rezerwy Federalnej [2009],
 	\emph{Notatka prasowa z dnia 18. marca 2009 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20090318a.htm}, Waszyngton, dostęp: styczeń 2017.	
\bibitem{Fed12}
 	System Rezerwy Federalnej [2010],
 	\emph{Notatka prasowa z dnia 3. listopada 2010 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20101103a.htm}, Waszyngton, dostęp: styczeń 2017.	
\bibitem{Fed13}
 	System Rezerwy Federalnej [2011],
 	\emph{Notatka prasowa z dnia 21. września 2011 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20110921a.htm}, Waszyngton, dostęp: styczeń 2017.
\bibitem{Fed14}
 	System Rezerwy Federalnej [2012],
 	\emph{Notatka prasowa z dnia 13. września 2012 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20120913a.htm}, Waszyngton, dostęp: styczeń 2017.
\bibitem{Fed15}
 	System Rezerwy Federalnej [2012],
 	\emph{Notatka prasowa z dnia 12. grudnia 2012 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20121212a.htm}, Waszyngton, dostęp: styczeń 2017.
\bibitem{Fed16}
 	System Rezerwy Federalnej [2013],
 	\emph{Notatka prasowa z dnia 18. grudnia 2013 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20131218a.htm}, Waszyngton, dostęp: styczeń 2017.
\bibitem{Fed17}
 	System Rezerwy Federalnej [2014],
 	\emph{Notatka prasowa z dnia 29. października 2014 roku},
 	\url{http://www.federalreserve.gov/newsevents/press/monetary/20141029a.htm}, Waszyngton, dostęp: styczeń 2017.
\bibitem{svensson02}
	Svensson L.O. [1994],
	\emph{Estimating Forward Interest Rates with the Extended Nelson and Siegel Method},
	Sveriges Riksbank Quarterly Review 1995:3, 13-26. 
\bibitem{swanson37}
	Swanson E. T. [2015],
	\emph{Measuring the Effects of Unconventional Monetary Policy on Asset Prices}, \url{http://www.nber.org/papers/w21816.pdf}, National Bureau of Economic Research, dostęp: styczeń 2015.
\bibitem{tahiri33}
	Tahiri S., Six J.M [2016],
	\emph{TLTRO II: The ECB Is Ready To Lend At Negative Rates}, \url{http://media.mhfi.com/documents/TLTRO-II.pdf}, Standard \& Poor's Rating Services, Nowy Jork, dostęp: styczeń 2017. 	
\bibitem{wen26}	 
	Wen Y. [2013],
	\emph{Evaluating Unconventional Monetary Policies - Why Aren't They More Effective?}, \url{https://research.stlouisfed.org/wp/2013/2013-028.pdf}, Federal Reserve Bank of St. Louis, Saint Louis, dostęp: styczeń 2017. 	
\end{thebibliography}